---
title: "Cabbages"
author: "Hannah B Vong!"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
# Load required packages
library(ggplot2)
library(dplyr)

data <- cabbages
```
  
# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: There is no difference in the Vitamine C content of cabbages bases on cultivation method

$H_A$: There is a difference in the Vitamin C content of cabbages based on cultivation method


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Vitamin C content is a numerical variable, cultivation method is a factor

```{r}
data = data

```


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
# Create a boxplot to visualize the data
ggplot(data, aes(x = Cult, y = VitC)) +
  geom_boxplot() +
  labs(title = "Boxplot of VitC by Cult")
  x = "Cult"
  y = "VitC"
```




### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
# Calculate summary statistics
summary_stats <- data %>%
group_by(Cult) %>%
summarise(
Mean = mean(VitC),
Median = median(VitC),
SD = sd(VitC)
)
summary_stats

```
Base on the graphical results  and the numerical result the average ascorbic acid content of cabbages grown using the c39 and c52 methods. According to the report , the average ascorbic acid content of cabbages grown using the c39 method is 51.5 units while that of cabbages grown using the c52 method is 64.4 units 23. This suggests that cabbages grown using the c52 method generally have higher ascorbic acid content than those grown using the c39 method.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
# Perform an ANOVA test to assess differences among groups within the factor variable
anova_result <- aov(VitC ~ Cult, data = data)
summary(anova_result)


```



# Discussion and Conclusion 
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


Based on the information provided in the previous message, we can conclude that cabbages grown using the c52 method generally have higher ascorbic acid content than those grown using the c39 method. However, we do not have any information on the statistical significance of this difference.
However, since we do not have access to the results of the t-test conducted on this dataset, we cannot provide any further information on this topic.
